Gut-resident microorganisms and their genes are associated with cognition and neuroanatomy in children

### 2023-10-03 manuscript/main.tex
added numbers to future experiment

While LMs did not identify any taxa in the 0-6 month range
that were associated with concurrently measured cognitive function,
we reasoned that developmental trajectories that begin
\textit{in utero} may not be immediately altered by
microbial exposures, such that microbial influences early in life
may take time to manifest. To test this hypothesis,
we asked whether RF models trained on taxonomic profiles
in the first year of life
could predict \textit{future} cognitive performance (Figure 3B, D).
Models were consistently able to learn microbial species that are associated
with cognitive performance at a future visit
(mean time between visits: XX, %TODO
mean test set correlation: YY).

>>>>

While LMs did not identify any taxa in the 0-6 month range
that were associated with concurrently measured cognitive function,
we reasoned that developmental trajectories that begin
\textit{in utero} may not be immediately altered by
microbial exposures, such that microbial influences early in life
may take time to manifest. To test this hypothesis,
we asked whether RF models trained on taxonomic profiles
in the first year of life
could predict \textit{future} cognitive performance (Figure 3B, D).
Models were consistently able to learn microbial species that are associated
with cognitive performance at a future visit
(mean time between visits: 21.5 months [sd = 9.9 months] (Figure 3C),
mean test set correlation: 0.27).
